%-------------------------
% Resume in Latex
% Author : Gabriel Sison
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor} % Required for custom colors
\usepackage{hyperref}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Define violet purple color to match website
\definecolor{violetpurple}{RGB}{124, 58, 237}
% Warm cream background tint
\definecolor{warmcream}{RGB}{255, 250, 245}
\pagecolor{warmcream}

% Define hyperlink color
\hypersetup{
    colorlinks=true, % Enable colored links
    linkcolor=violetpurple,  % Color of internal links (sections, pages etc.)
    urlcolor=violetpurple,   % Color of external links
}

\newcommand{\betterHref}[2]{\href{#1}{\color{violetpurple}{#2}}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\extraDegree}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-3pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        % NAME
        {\huge\scshape Saurabh Shah} 
        % SUBHEADING
        % \\ Machine Learning Research Engineer\\

        \small
        % WEBSITE
        \href{https://saurabhs.site/}{\raisebox{-0.2\height}\faGlobe\  \underline{saurabhs.site}} ~
        % EMAIL
        \href{mailto:saurabh@humansand.ai}{\raisebox{-0.2\height}\faEnvelope\  \underline{saurabh@humansand.ai}} ~ 
        % LINKEDIN
        \href{https://www.linkedin.com/in/saurabh-shah-90063a18a}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
        % GITHUB
        \href{https://github.com/saurabh111233212}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
        % GOOGLE SCHOLAR
        \href{https://scholar.google.com/citations?hl=en&user=iB_qEXkAAAAJ}{\raisebox{-0.2\height}\faGoogle\ \underline{Google Scholar}}
    \end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
    % MAIN INFORMATION
    \resumeSubheading
    {University of Pennsylvania}{Philadelphia, PA}
    {Master of Science in Engineering in Computer Science 3.91 GPA}{Jan 2021 - May 2023}
        % BULLET POINTS
        \resumeItemListStart
            \resumeItem{Focused on Algorithmic Theory, Artificial Intelligence, Machine Learning, and Natural Language Processing (NLP)}
        \resumeItemListEnd
    \extraDegree
    {Bachelor of Science in Engineering in Networked and Social Systems Engineering 3.90 GPA}{Aug 2019 - May 2023}
        % BULLET POINTS
        \resumeItemListStart
            \resumeItem{Major combines Computer Science, Systems Engineering, and Economics. Minors in Data Science and Mathematics}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
        {humans\&}{San Francisco, CA}
            % POSITION 1
            {Member of Technical Staff}{Jan 2026 - Present}
            \resumeItemListStart
                \resumeItem{Training systems that work with people, not replace them}
            \resumeItemListEnd

    \resumeSubheading
        {Allen Institute for AI (Ai2)}{Seattle, WA}
            % POSITION 1
            {Research Engineer \betterHref{https://arxiv.org/abs/2512.13961}{(paper)}}{Feb 2025 - Jan 2026}
            \resumeItemListStart
                \resumeItem{\betterHref{https://allenai.org/olmo}{Olmo} team. Trained Olmo 3 to write code, use tools, and reason. Built RL + code execution infra. Code data curation.}
            \resumeItemListEnd
    
        % COMPANY 1
        \resumeSubheading
        {Apple}{Seattle, WA}
            % POSITION 1
            {Machine Learning Engineer}{Oct 2023 - Feb 2025}
            \resumeItemListStart
                \resumeItem{Siri Natural Language Understanding (NLU). Helped build an agentic Siri planner powered by Apple Intelligence}
                % \resumeItem{ML: Trained and evaluated LoRA adapters of the planner for cross-domain personal search queries \betterHref{https://www.youtube.com/watch?v=TPe8revsg3k}{(link)}}
                % \resumeItem{SWE: (1) Lead the development of a streamlined evaluation platform. (2) Supported annotation data pipelines} 
            \resumeItemListEnd

        % COMPANY 2
        \resumeSubheading
        {Allen Institute for AI (Ai2)}{Seattle, WA}
            % POSITION 1
            {Research Engineering Intern \betterHref{https://arxiv.org/abs/2402.00838}{(paper)}}{Aug 2023 - Oct 2023}
            \resumeItemListStart
                \resumeItem{Tried pretraining \betterHref{https://allenai.org/olmo}{Olmo} with \betterHref{https://arxiv.org/abs/2307.05695}{ReLoRA}, a parameter-efficient \textit{pretraining} method. Learned lots about PyTorch/FSDP}
            \resumeItemListEnd
        % COMPANY 3
        \resumeSubheading
        {University of Pennsylvania}{Philadelphia, PA}
            % POSITION 1
            {Researcher \betterHref{https://arxiv.org/abs/2305.04990}{(paper)} \betterHref{https://www.youtube.com/watch?v=I0P5XbYqGq0\&ab_channel=SaurabhShah}{(talk)}}{Aug 2022 - May 2023}
            \resumeItemListStart
                \resumeItem{Explored using free-text explanations for improving the robustness of LLMs to spurious cues in training data}
            \resumeItemListEnd
            
        \resumeSubheading
        {Apple} {Seattle, WA}
            {Machine Learning Engineering Intern} {May 2022 - Aug 2022}
            \resumeItemListStart
                \resumeItem{Siri NLU. Built an internal Swift iOS app for testing text-to-intent parsing and counterfactual evaluation}
            \resumeItemListEnd

        \resumeSubheading
        {Amazon} {Nashville, TN}
        {Software Development Engineering (SDE) Intern} {May 2021 - Aug 2021}
        \resumeItemListStart
            \resumeItem{Robotics-AI Computer Vision. Built a web app with React and AWS to configure, search, and view over 300,000 cameras}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Projects} 
    \resumeSubHeadingListStart
        \resumeProjectHeading {The Learning Curve
        \betterHref{https://learnycurve.substack.com}{(link)}
        }
        {March 2025 - Present}
        \resumeItemListStart
        \resumeItem{A blog where I talk about machine learning research and engineering}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {Griffin LM + CUDA \betterHref{https://github.com/saurabh111233212/griffin_reimpl}{(link)}} 
        % Date
        {May 2024 - August 2024}
        \resumeItemListStart
        \resumeItem{I learned some cuda \betterHref{https://github.com/saurabh111233212/programming_massively_parallel_processors}{(link)} and tried to implement \betterHref{https://arxiv.org/abs/2402.19427}{Griffin} from scratch in PyTorch with a cuda extension for the scan}
        \resumeItemListEnd

        % Project 2
        \resumeProjectHeading
        {Concept Space Embeddings \betterHref{https://github.com/saurabh111233212/ConceptTrees}{(link)}}
        % Date
        {Feb 2023 - Apr 2023}
        \resumeItemListStart
            \resumeItem{Worked with a team of 2 to create a novel method for interpretable embeddings of arbitrary text using LLMs and Decision Trees. Works for classification, regression, clustering, and post hoc explanation of black box models}
        \resumeItemListEnd

        \resumeProjectHeading{Compass (Penn Course Recommendation) \betterHref{https://github.com/saraxstrenger/seniordesign}{(link)}}
        {Jan 2023 - Apr 2023}
        \resumeItemListStart
            \resumeItem{Group of 4. Course recommendation web app. I built the recommendation system with (1) collaborative filtering and (2) text embeddings to recommend courses to students based on (1) perceived difficulty and (2) natural language interests}
        \resumeItemListEnd

        \resumeProjectHeading{Poké-GANs (Pokémon Generator) \betterHref{https://github.com/saurabh111233212/PokeGANs}{(link)}}
        {Mar 2022 - Apr 2022}
        \resumeItemListStart
            \resumeItem{Generated complete Pokémon from names. Fine-tuned GPT-3 for types, stats, abilities; CLIP+VQGAN for images from generated text. Trained custom LSTM and GANs from scratch and compared results. Worked with partner.}
        \resumeItemListEnd

        \resumeProjectHeading{Comedy Bot \betterHref{https://github.com/saurabh111233212/comedybot}{(link)}}
        {July 2020}
        \resumeItemListStart
            \resumeItem{Experimented with ML models to recognize and rate jokes I write and perform for crowds of 150+. Joke datasets from Kaggle. Experimented with Bag of Words/Naïve Bayes and LSTM models. Built with PyTorch}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Technical Skills  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
    \vspace{-7pt}
    \begin{itemize}
    [leftmargin=0.15in, label={}]\small{\item{
        % LANGUAGES
        \textbf{Languages}{: Python, TypeScript/JavaScript, Go, CUDA/C++, Java, Haskell, Coq, Swift} \\
        % TECHNOLOGIES
        \textbf{Technologies/Frameworks}{: PyTorch/FSDP, LLMs, HuggingFace, AWS, React, Pandas} \\}}
    \end{itemize}
 
\end{document}
